Usable Security in Virtual Power Plants

### 2018-01-24 acmart-master/draft.tex
More changes

Critical infrastructures are integral to the functioning of our daily lives. They are changing in order to solve different problems it faces nowadays. The growth of power demand, integration of markets and the need of sustainable and efficient energy sources. \\
One such important critical infrastructure is the energy grid. A typical energy grid is divided into several domains such as generation, transmission and distribution. All the actors within domains of a energy grid are connected through information and communication technology(ICT). Hence, energy grids have continuously been the target of cyber attacks and provided their use of standard architecture and internet, they are relatively easier to attack. Security mechanisms have been introduced to protect against such attacks. Security-by-design approach has been used to determine security measures for various systems during design phase. With this approach, the system is equipped to deal with difficult scenarios before deployment. \\ However, there may be instances where the user must intervene to control the system when under attack and stress. During such instances, the user maybe asked to re-authenticate themselves, at which point remembering increasingly difficult passwords and entering it correctly actually causes an overhead on the user. The security mechanism in fact is a hindrance here. Such a situation could be avoided if the authentication system in place is usable under different conditions.
%Intro big pic, narrow, Related work seperate subsection

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model using security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems\cite{nurse2011guidelines}. Standards such as ISO 9241-11\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system. A first look at such a relation is provided\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase\cite{nielsen1992usability}. The goal of this research to establish how usability of security in power plants can be achieved. A second goal is to reduce the burden on a power plant operator, since operation of a plant can be stressful. We assume that the operator of the power plant is oblivious to the security design. We shall focus only on security and usability and their relation. Hence, usability of other systems are not considered. Only systems having an user interface are considered.

@@

The availability of electric power is the primary goal of the power grids. As the smart grid develops, these power systems are more sophisticated, using modern technology allowing better control and reliability. Smart grid will feature a highly interconnected network, opening up the possibility for new vulnerabilities.\\

@@

Virtual Power Plant(VPP) is one such infrastructure. A VPP is a centralized system that aggregates various energy sources to meet the energy demand of a geographical area. It relies upon software to remotely control, optimize and dispatch energy from Distributed Energy resources(DERs). At the heart of every VPP is the Energy Management System(EMS). The EMS manages power flows in order to minimize the electricity generation costs and avoid loss of energy produced by generators based on renewable energy sources. The EMS consists of a set of software programs designed to control and monitor several aspects of the power plant such as generation levels, capacity, current and voltage levels, power fluctuations, supply-demand matching and so on. These software programs are automated and carry out operations based on pre-defined rules and functions. They are consistently monitored by an operator, known as VPP Operator. Therefore, a VPP is a system that employs software and networking tools making it susceptible to cyber attacks. There are several known ways to attack a power plant, network based attacks such as man-in-the-middle, Masquerading, Spoofing, Denial of service, Injection etc, software vulnerability based attacks, hardware based attacks and so on. Most of the known attacks have defined countermeasures which are in use to protect the power plant. Even with the presence of an extensive defense infrastructure, there may be new and unprecedented attacks on power plants, including those that exploit zero-day vulnerabilities. 
\newline
A virtual power plant under attack is expected to continue functioning normally, i.e, it must primarily meet the goal of energy supply to the customer end. In anticipation of such attacks, the system may be configured to reschedule, find replacement sources or even attempt to control the system to prevent its shutdown or damage. The operator may be requested to control the system in case of unprecedented events or cases where the operator's intervention or authorization are required. For example, consider a scenario when a power plant is under attack and its primary generation units are inaccessible. The VPP then attempts to find replacement units. However, in case of a large scale attack units in the neighbourhood may also be rendered inaccessible. Therefore, the VPP may have to look for units outside its allotted area which may require operator request and authorization. In such a case, the operator is required to access and operate the system. We assume there is an authentication mechanism in place that protects the system from unauthorized access, and therefore is the first interface the operator comes across. This authentication interface is vital since it prevents unauthorized personnel from accessing the system either in normal system state or when the system is under attack, which could be orchestrated by the unauthorized personnel themselves. The authentication mechanism should however be a usable mechanism, even under stress, to prevent the legitimate power plant operator from being locked out. A traditional username-password system in this case could potentially be a problem. The operator is required to recall and enter the information accurately in order to be granted access. In such a situation, the operator may find it difficult to recall a complex password and is more likely to make mistakes entering it and being denied access, which could lead to a catastrophe.

@@

Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. It provides a measure of security for guarding access to important information, such as your online banking account. 
Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly. 
Some accounts may have a relatively weak password, because of the cost of undue information leakage or harm to the owner if the account is compromised. Other accounts might have a stronger password because users don't want their money siphoned off by a cyber-criminal. These are judgements about the perceived value of the information. \\
Passwords are also exceptionally susceptible to dictionary and brute force attacks. Simple passwords can be cracked in seconds and longer passwords that include common words and phrases from literature take up to a week to be cracked. Passwords can be called secure if the time required to crack is sufficiently long, such as in years or decades. Such passwords may be constructed from a combination of alphabets, numbers and symbols. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. Users tend to create variations of their previous passwords to prevent having to generate a new password and consider using a variant of a previous password easier since they are already familiar with it. This is especially problematic since users may forget the password has been changed and do not remember the new password, inviting a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Therefore, the most secure passwords and password systems are, in fact, the least usable.

@@

Usability depends on a number of factors including how well the functionality fits the user needs, how well the flow through the application fits user tasks and how well the response of the application fits user expectations. We can learn to be better user interface designers by learning design principles and design guidelines. But even the most insightful designer can only create a highly-usable system through a process that involves getting information from people who actually use the system. Usability is the quality of a system that makes it easy to learn, easy to use, easy to remember, error tolerant, and subjectively pleasing.

@@

From the user's perspective, usability is important because it can make the difference between performing a task accurately and completely or not, and enjoy the process or be frustrated. From the developer's perspective, usability is important because it can mean the difference between the success or failure of a system. From a management point of view, software with poor usability can reduce the productivity of the workforce to a level of performance worse than without the system. In all cases, lack of usability can cost time and effort and can greatly determine the success or failure of a system. Given a choice, people tend to buy systems that are more user-friendly.

The key principle for maximizing usability is to employ iterative design, which progressively refines the design through evaluation from the early stages of design. The evaluation steps enable the designers and developers to incorporate user and client feedback until the system reaches an acceptable level of usability.\\

The preferred method for ensuring usability is to test actual users on a working system. Achieving a high level of usability requires focusing design efforts on the intended end-user of the system. There are many ways to determine who the primary users are, how they work, and what tasks they must accomplish. However, clients' schedules and budgets can sometimes prevent this ideal approach. Some alternative methods include user testing on system prototypes, a usability audit conducted by experts, and cognitive modelling.

Usability is one of the focuses of the fields of Human Factors Psychology and Human-Computer Interaction. As the name suggests, usability has to do with bridging the gap between people and machines. A user interface (or human-computer interface) refers to the parts of a hardware and/or software system that allows a person to communicate with it. This includes output devices (the way the computer communicates with a user) and input devices (the way a user communicates with the computer). Typical "output devices" include computer monitors and the operating systems that run on them, and also include speakers and other devices that provide feedback. "Input devices" include peripherals like keyboards, mice, and joysticks, and also include microphones and eye movement devices. Each of these interface components has devices corresponding to the visual (sight), aural (sound), and haptic(touch) channels of the brain. Usability engineering studies these elements of the user's experience.

@@

\section{Framework for Usable Security}
In the previous section, usability was explained as a broad concept. It is applicable to any system which is directly interfaced by a user or has an impact on user perforamnce. In this section, we specialize the usability concept to security systems and as will further be explained, to authentication mechanisms.\\ Since, usability and security are normally at opposite ends of the spectrum, there are no uniform set of criteria or guidelines that define a usable security system. Nurse et al\cite{nurse2011guidelines} 
compiled a list as guidelines for usable security.
\newline
To design a security system that is usable, we need appropriate metrics to measure its efficiency. Therefore, we need to define such metrics. With the security system in focus, the usability metrics must stem from the properties of security themselves. Through this process, we then develop a security with a view of usability in the design stage itself, rather than first building a security system and then attempting to incorporate usability. When designing a security system, each component of security, every module could be tested for its usability wherever applicable. Usability of one component may affect that of another. That is, if a component is less usable, the overall usability of the system reduces, since the user may spend more resources on such a component at the cost of others. In other words, it hinders the performance of the system as a whole. The issue at hand is that due to the lack of usability metrics or any quantifiable value, any system cannot yet be defined as usable or unusable. \\

@@

Usability of a system, though determined by efficiency, effectiveness and satisfaction, is still not quantified. Furthermore, the three properties can be measured in various ways for different systems. To specialize usability for a security system, a relation between security and usability must be established. In the presence of such a relation, a security system's properties can be optimized, via metrics, such that usability properties are satisfied. \textit{This method can be used to integrate usability into any system instead of security systems.} \\

In essence, each property has a metric with a desirable value that makes the system usable. But these metrics are defined when a system operates in normal mode. When in any situation other than normal mode, these metrics may vary and the system will have to adapt to the situation. This variation could be used as an indication of how usable the system is. A security system will have to go through a usability engineering cycle subject to constraints and metrics. To achieve strong security, security engineering must begin parallel to system development, which is known as security-by-design. Similarly, usability must be considered in the design phase as well. Individual components may be evaluated for usability. This may be considered as \textbf{Usable Security by Design.}

@@

\begin{center}
\begin{table}[H]
\caption{Relation between security and usability}
\label{tab:security-usability-relation}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|c|} 
\hline
\multicolumn{2}{| c |}{\textbf{Usability}}
& \textbf{Security} \\
\hline
\textbf{Factors and Properties} & \textbf{Criteria/Requirements} & \textbf{Factors and Properties} \\
\hline
Effectiveness & Accuracy & EER, Accuracy \\
\hline
Efficiency & Minimal Action & \makecell{Task Completion Time, \\ Monetary cost of performing the task} \\
\hline
{Satisfaction} & {Operability, Minimal Action} &  {Interface Design} \\
\hline
Productivity & Memory Load & Authentication Token \\
\hline
Learnability & \makecell{Time to learn functionalities,\\ Minimal Action} &  Interface Design \\
\hline
\end{tabular}
}
\end{table}
\end{center}

The second column in table \ref{tab:security-usability-relation} specifies the requirements(or criteria) for usability of a security system. These criteria were specifically selected for a scenario involving a user attempting to gain access through an authentication mechanism. These requirements need to be quantified with metrics for an evaluation. the table \ref{tab:possible-values} shows the metrics and the desired values for this specific use case.

\begin{center}
\begin{table}[H]
\caption{Possible values for metrics}
\label{tab:possible-values}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Permissible Range} \\
\hline
EER & As low as possible, tending to 0\\
\hline
Accuracy (Success Rate of Correct Input) & ~100\%. \\
\hline
Task Completion Time & Time in seconds; Depends on use case \\
\hline
Interface Design & User rating based on satisfaction and feedback\\
\hline
Memory Load & User rating based on satisfaction and feedback\\
\hline
\end{tabular}
}
\end{table}
\end{center}

Therefore, a \textit{usable security framework for an authentication system} consists of an authentication system which includes a user-friendly interface, requires a user to have minimalistic or easy to use authentication tokens, satisfies the criteria for a conventional security system such as Confidentiality, Integrity and Availability in addition to all the usability factors mentioned in \ref{tab:security-usability-relation}. The evaluation of these factors via usability criteria with respect to their metrics should fall in the permissible zone. The user also must provide feedback and specify the drawbacks, if any and suggestions to improve the system from the perspective of usability. \\
The factors mentioned in the third column are specific to authentication mechanisms. If usability was being considered for any other system, the respective factors would be derived and placed accordingly in that column. For example, consider an organization attempting to develop self-driving automobiles. User experience plays a big part in such an inventive technology. To measure usability of such vehicles, effectiveness will be determined by the performance of the vehicle. It is up to the discretion of the organization to determine which metric they would prefer to use to measure the performance. An example could be speed or acceleration. Efficiency can be measured by fuel consumption. Satisfaction can be measured by user feedback. In this way, the framework could be used for any system.

\subsection{Using The Framework}
To use the usable security framework, the organization intending to use it has to specify the goals on the system. Similar systems may be optimized in different ways, hence the developers need to specify their priorities. The important factors and properties affecting the system must be listed and with respect to the priorities, i.e, goals of the system and the developers, those factors affecting the user most should be selected. For example, let the goal be a highly user-friendly yet efficient authentication mechanism. Therefore, Interface Design and Time as a resource are goals and are priorities.\\
The usability framework, with the help of QUIM, breaks down usability factors into criteria that can be quantified. Those usability factors that are of importance to the developers must be focused upon, however, the three usability factors, efficiency, effectiveness and satisfaction must all be used to satisfy usability, as per ISO 9241-11. In our example, task completion time and memory load will be the focus and hence it will need to be optimized.\\
In the next step, those factors derived from the target system must be used as quantifiable values to measure the criteria specified in table \ref{tab:security-usability-relation}. If a criteria cannot be quantified, alternative criteria can be selected from the QUIM usability criteria. In any case, the prioritized factors must be quantified. In our example, accuracy is a measurable quantity of the system as well as the usability criteria used to determine the efficiency.\\
Accordingly, the factors measured from the system must be used to quantify the usability criteria, which help measure the usability factors.

@@

\begin{center}
\begin{table}[H]
\caption{Results for Biometric systems.}
\label{tab:result1}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Observed values} \\
\hline
EER & 3.9\%\\
\hline
Accuracy (Success Rate of Correct Input) & 96.1\%. \\
\hline
Task Completion Time & Average of 1.8 seconds \\
\hline
Interface Design & 4.2\\
\hline
Memory Load & 5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

@@

\begin{center}
\begin{table}[H]
\caption{Results for password based systems.}
\label{tab:result2}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|c|}
\hline
\textbf{Security Metric} & \textbf{Expected values} & \textbf{Observed values} \\
\hline
Accuracy (Success Rate of Correct Input) & 100\% & 100\%. \\
\hline
Task Completion Time & 10-12 seconds & Avg of 12.2 seconds \\
\hline
Interface Design & >4 & 4.7\\
\hline
Memory Load & >4 & 3.5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

>>>>

Critical infrastructures are integral to the functioning of our daily lives. They are changing in order to solve different problems it faces nowadays. The growth of power demand, integration of markets and the need of sustainable and efficient energy sources. \\
One such important critical infrastructure is the smart grid. A typical smart grid is divided into several domains such as generation, transmission and distribution. All the actors within domains of a smart grid are connected through information and communication technology(ICT). Hence, energy grids have continuously been the target of cyber attacks and provided their use of standard architecture and internet, they are relatively easier to attack. Security mechanisms have been introduced to protect against such attacks. Security-by-design approach has been used to determine security measures for various systems during design phase. With this approach, the system is equipped to deal with difficult scenarios before deployment. \\ However, there may be instances where the operator must intervene to control the system when under attack and stress. During such instances, the user maybe asked to re-authenticate themselves, at which point remembering increasingly difficult passwords and entering it correctly actually causes an overhead on the operator. The security mechanism in fact is a hindrance here. Such a situation could be avoided if the authentication system in place is usable under different conditions.

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model using security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems\cite{nurse2011guidelines}. Standards such as ISO 9241-11\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system. A first look at such a relation is provided\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase\cite{nielsen1992usability}. The goal of this research to establish how usability of security in power plants can be achieved. A second goal is to reduce the burden on a power plant operator, since the operation of a power plant can be stressful. We assume that the operator of the power plant is oblivious to the security design. Additionally, we assume there is an authentication system in place whose goal is to protect the system and authenticate legitimate operators and is expected to function with high efficiency. We shall focus only on security and usability and their relation. Hence, usability of other systems are not considered. Only systems having an user interface are considered.

@@

The availability of electric power is the primary goal of the smart grids. As the smart grid develops, these power systems are more sophisticated, using modern technology allowing better control and reliability. Smart grid will feature a highly interconnected network, opening up the possibility for new vulnerabilities.\\

@@

Virtual Power Plant(VPP) is one such infrastructure. A VPP is a centralized system that aggregates various energy sources to meet the energy demand of a geographical area. It relies upon software to remotely control, optimize and dispatch energy from Distributed Energy resources(DERs). At the heart of every VPP is the Energy Management System(EMS). The EMS manages power flows in order to minimize the electricity generation costs and avoid loss of energy produced by generators based on renewable energy sources. The EMS consists of a set of software programs designed to control and monitor several aspects of the power plant such as generation levels, capacity, current and voltage levels, power fluctuations, supply-demand matching and so on. These software programs are automated and carry out operations based on pre-defined rules and functions. They are consistently monitored by an operator, known as VPP Operator. Therefore, a VPP is a system that employs software and networking tools making it susceptible to cyber attacks. There are several known ways to attack a power plant, network based attacks such as man-in-the-middle, Masquerading, Spoofing, Denial of service, Injection etc, software vulnerability based attacks, hardware based attacks and so on. Most of the known attacks have defined countermeasures which are in use to protect the power plant. Even with the presence of an extensive defense infrastructure, there may be new and unprecedented attacks on power plants, including those that exploit zero-day vulnerabilities. 
\newline
A virtual power plant under attack is expected to continue functioning normally, i.e, it must primarily meet the goal of availability to the customer end. In anticipation of such attacks, the system may be configured to reschedule, find replacement sources or even attempt to control the system to prevent its shutdown or damage. The operator may be requested to control the system in case of unprecedented events or cases where the operator's intervention or authorization are required. For example, consider a scenario when a power plant is under attack and its primary generation units are inaccessible. The VPP then attempts to find replacement units. However, in case of a large scale attack units in the neighbourhood may also be rendered inaccessible. Therefore, the VPP may have to look for units outside its allotted area which may require operator request and authorization. In such a case, the operator is required to access and operate the system. We assume there is an authentication mechanism in place that protects the system from unauthorized access, and therefore is the first interface the operator comes across. This authentication interface is vital since it prevents unauthorized personnel from accessing the system either in normal system state or when the system is under attack, which could be orchestrated by the unauthorized personnel themselves. The authentication mechanism should however be a usable mechanism, even under stress, to prevent the legitimate power plant operator from being locked out. A traditional username-password system in this case could potentially be a problem. The operator is required to recall and enter the information accurately in order to be granted access. In such a situation, the operator may find it difficult to recall a complex password and is more likely to make mistakes entering it and being denied access, which could lead to a catastrophe.

@@

Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly. 
Secure passwords may be constructed from a combination of alphabets, numbers and symbols. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. Users tend to create variations of their previous passwords to prevent having to generate a new password and consider using a variant of a previous password easier since they are already familiar with it. This is especially problematic since users may forget the password has been changed and do not remember the new password, inviting a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Therefore, the most secure passwords and password systems are, in fact, the least usable.

@@

Usability depends on a number of factors including how well the functionality fits the user needs, how well the flow through the application fits user tasks and how well the response of the application fits user expectations. For a power plant operator, the system must be easy to understand and easy to use. The operator is not expected to understand how the system is built or functions, but is expected to interface well with the said system. 
\newline
From a plant operator's perspective, usability is important because it can make the difference between performing a task accurately and completely or not. From the developer's perspective, usability is important because it can mean the difference between the success or failure of a system. From a management point of view, software with poor usability can reduce the productivity of the workforce to a level of performance worse than without the system. In all cases, lack of usability can cost time and effort and can greatly determine the success or failure of a system.

@@

The key principle for maximizing usability is to employ iterative design, which progressively refines the design through evaluation from the early stages of design. The evaluation steps enable the designers and developers to incorporate user and client feedback until the system reaches an acceptable level of usability. Achieving a high level of usability requires focusing design efforts on the intended end-user of the system. Power Plant operator feedback will be vital. Due to the fact that the operators manage a critical infrastructure, their feedback will be different and more specific when compared to other systems. A step forward would be to take the existing system, consider the operator feedback on usability and task information together to build a usable security framework.

@@

\section{Framework for Usable Security}
In the previous section, usability was explained as a broad concept. It is applicable to any system which is directly interfaced by a user or has an impact on user perforamnce. In this section, we specialize the usability concept to security in virtual power plants and as will further be explained, to authentication mechanisms.\\ Since, usability and security are normally at opposite ends of the spectrum, there are no uniform set of criteria or guidelines that define a usable security system. Nurse et al\cite{nurse2011guidelines} compiled a list as guidelines for usable security.
\newline
To design a security system that is usable, we need appropriate metrics to measure its performance, especially in context of virtual power plants. Therefore, we need to define such metrics. With the security system in focus, the usability metrics must stem from the properties of security themselves. Since the security system is designed for virtual power plants, some factors are automatically constrained. Due to the volatile nature of power plants, time is of utmost importance. Hence, a time efficient system is a requirement. We also need to consider the performance of the operator under stress. A well designed system reduces operator responsibilities like memory use for passwords and encourages productivity. Through this process, we then develop a security with a view of usability in the design stage itself, rather than first building a security system and then attempting to incorporate usability. When designing a security system, each interface of security could be tested for its usability wherever applicable. A less usable component may affect usability of another. The issue at hand is that due to the lack of usability metrics or any quantifiable value, any system cannot yet be defined as usable or unusable. \\

@@

Usability of a system, though determined by efficiency, effectiveness and satisfaction, is still not quantified. Furthermore, the three factors can be measured in various ways for different systems. To measure these factors, a relation between security and usability must be established. In the presence of such a relation, a security system's properties can be optimized, via metrics, such that usability properties are satisfied. \textit{This method can be used to integrate usability into any system instead of security systems.} In essence, each property has a metric with a desirable value that makes the system usable. A security system will have to go through a usability engineering cycle subject to constraints and metrics. To achieve strong security, security engineering must begin parallel to system development, which is known as security-by-design. Similarly, usability must be considered in the design phase as well. Individual components may be evaluated for usability. This may be considered as \textbf{Usable Security by Design.}

@@

\begin{center}
\begin{table*}
\caption{Relation between security and usability}
\label{tab:security-usability-relation}
\resizebox{14cm}{!}{
\begin{tabular}{|c|c|c|} 
\hline
\multicolumn{2}{| c |}{\textbf{Usability}}
& \textbf{Security} \\
\hline
\textbf{Factors and Properties} & \textbf{Criteria/Requirements} & \textbf{Factors and Properties} \\
\hline
Effectiveness & Accuracy & EER, Accuracy \\
\hline
Efficiency & Minimal Action & \makecell{Task Completion Time, \\ Monetary cost of performing the task} \\
\hline
{Satisfaction} & {Operability, Minimal Action} &  {Interface Design} \\
\hline
Productivity & Memory Load & Authentication Token \\
\hline
Learnability & \makecell{Time to learn functionalities,\\ Minimal Action} &  Interface Design \\
\hline
\end{tabular}
}
\end{table*}
\end{center}

The second column in table \ref{tab:security-usability-relation} specifies the requirements(or criteria) for usability of a security system. These criteria were specifically selected for a scenario involving a user attempting to gain access through an authentication mechanism. These requirements need to be quantified with metrics for an evaluation. the table \ref{tab:possible-values} shows the metrics and the desired values for this specific use case. In power plants, it is undesirable to lock the operator out of the system. Therefore we need a highly accurate and efficient system, hence an accuracy as close as possible to 100\% and an EER, in case of biometric systems, as low as possible is desirable. We do not want the operator to be stressed while waiting for authentication, hence a fast system is needed. Both Interface Design and Memory Load can be rated by the operator based on scale from 1 to 5, where 1 is "Very Uncomfortable" and 5 is "Very Comfortable". The operator must be comfortable with using the system and must also not expend too much memory to prevent stress. Both metrics should be placed 4 or more.

\begin{center}
\begin{table}
\caption{Possible values for metrics}
\label{tab:possible-values}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Permissible Range} \\
\hline
EER & \textasciitilde 0\%\\
\hline
Accuracy  & \textasciitilde 100\%. \\
\hline
Task Completion Time &  8-10 seconds \\
\hline
Interface Design & >4\\
\hline
Memory Load & >4\\
\hline
\end{tabular}
}
\end{table}
\end{center}

Therefore, a \textit{usable security framework for an authentication system} consists of an authentication system which includes a user-friendly interface, requires a user to have minimalistic or easy to use authentication tokens, satisfies the criteria for a conventional security system such as Confidentiality, Integrity and Availability in addition to all the usability factors mentioned in \ref{tab:security-usability-relation}. The evaluation of these factors via usability criteria with respect to their metrics should fall in the permissible zone. The operator also must provide feedback and specify the drawbacks, if any and suggestions to improve the system from the perspective of usability. \\
The factors mentioned in the third column are specific to authentication mechanisms. If usability was being considered for any other system, the respective factors would be derived and placed accordingly in that column. For example, consider an organization attempting to develop self-driving automobiles. User experience plays a big part in such an inventive technology. To measure usability of such vehicles, effectiveness will be determined by the performance of the vehicle. It is up to the discretion of the organization to determine which metric they would prefer to use to measure the performance. An example could be speed or acceleration. Efficiency can be measured by fuel consumption. Satisfaction can be measured by user feedback. In this way, the framework could be used for any system.

\subsection{Using The Framework}
To apply the usable security framework, the organization intending to use it has to specify the goals on the system. Similar systems may be optimized in different ways, hence the developers need to specify their priorities based on context of use. The important factors and properties affecting the system must be listed and with respect to the priorities, i.e, goals of the system and the developers, those factors affecting the user most should be selected. For example, let the goal be a highly user-friendly yet efficient authentication mechanism for power plant. Therefore, Interface Design and Time as a resource are goals and are priorities.\\
The usability framework, with the help of QUIM, breaks down usability factors into criteria that can be quantified. Those usability factors that are of importance to the developers must be focused upon, however, the three usability factors, efficiency, effectiveness and satisfaction must all be used to satisfy usability, as per ISO 9241-11. In our example, task completion time and memory load will be the focus and hence it will need to be optimized.\\
In the next step, those factors derived from the target system must be used as quantifiable values to measure the criteria specified in table \ref{tab:security-usability-relation}. If a criteria cannot be quantified, alternative criteria can be selected from the QUIM usability criteria. In any case, the prioritized factors must be quantified. In our example, accuracy is a measurable quantity of the system as well as the usability criteria used to determine the efficiency.\\
Accordingly, the factors measured from the system must be used to quantify the usability criteria, which help measure the usability factors.

@@

\begin{center}
\begin{table}[H]
\caption{Results for Biometric systems.}
\label{tab:result1}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Observed values} \\
\hline
EER & 3.9\%\\
\hline
Accuracy & 96.1\%. \\
\hline
Task Completion Time & Average of 1.8 seconds \\
\hline
Interface Design & 4.2\\
\hline
Memory Load & 5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

@@

\begin{center}
\begin{table}[H]
\caption{Results for password based systems.}
\label{tab:result2}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|c|}
\hline
\textbf{Security Metric} & \textbf{Observed values} \\
\hline
Accuracy & 100\%. \\
\hline
Task Completion Time & Avg of 12.2 seconds \\
\hline
Interface Design & 4.7\\
\hline
Memory Load & 3.5\\
\hline
\end{tabular}
}
\end{table}
\end{center}
